Conflict Driven Evolution and Urban Development: \\ Evidence from the Holy Roman Empire\footnote{ I thank Lara Andermann, Leonie Bielefeld, Daniel Bursian, Davide Cantoni, Emilio Esguerra, Filip Milojevic, Johannes Vorbach and Matthias Weigand for helpful comments and feedback. }

### 2023-06-26 paper/paper.tex
#29 include extra table
#29 appendix numbering
#29 finish More robustness

The raw \textit{Territorial Histories} dataset starts out with 1,471,934 yearly observations, of which I lose a small number while coding switches. I aggregate the rest into 30,980 observations with 50-year spacing. Of these I drop 16,110 that are not covered by the construction data. Finally, following \cite{schoenholzer2022}, for the baseline versions of all specifications I restrict the sample to cities with no more than two lifetime switches.\footnote
{
I relax this restriction in a robustness check.
} 
This removes another 9,975 observations, leaving 6,635 in the baseline sample.

@@

While this result may seem like evidence for omitted variable bias in the baseline estimate, that explanation is ultimately not plausible. To cause bias in Column (1) conflict incidents would need to be correlated both with the post-$Conquest$ dummy and with construction --- however, we can see that the latter is not the case: the coefficients on $Conflict$ in Columns (3) and (4) are tiny and not significant by any stretch of the imagination.\footnote
{
The coefficients on $Conflict$ in Table \ref{tab:controls_50y} are conditional correlations. Simply computing the correlation coefficient between the dummies for conflict incidents and for construction yields a value of $-0.01$.
} 
Rather, I suggest that the estimates for $\theta_{conquest}$ are different because they are estimated on different samples. More than two thirds of observations are lost between Columns (2) and (3) because of missing values in the $Conflict$ variable. Figure \ref{fig:conflict_map} shows that the remaining observations follow quite a different distribution across space --- if the spatial composition of the smaller sample was the same, the entire map would be a uniform shade. Instead we see big discrepancies: the west, the south, and Brandenburg retain 30\% to 60\% of their observations, while many northern and eastern regions all but vanish from the sample.

If we accept that the difference between the $\theta_{conquest}$ coefficients in (1) and (3) is due to the different spatial distribution of the sample, that has the interesting implication of spatially heterogeneous treatment effects. The null effect in (1) could be an average of the negative effect in the southwest and a hypothetical positive effect in the northeast. Outsiders could play a role, in a similar vein to \cite{levine2021, levine2022}'s theory --- the south and the west are bordered by the Habsburg Empire and France, two stable major powers, while the northeast is somewhat sheltered by the North Sea, the Baltic Sea, and the territory that comprises 1937 Poland, which was fragmented throughout much of its history.\footnote
{
Of course, England and Sweden would attack via the North and Baltic seas, but it seems a reasonable assumption that competition for territory would be more intense between states that share a land border.
} 
\cite{cervellati2022} BLANK. I leave this for future research to explore.

I conduct a number of other robustness checks.

@@

\section*{Appendix}

>>>>

The raw \textit{Territorial Histories} dataset starts out with 1,471,934 yearly observations, of which I lose a small number while coding switches. I aggregate the rest into 30,980 observations with 50-year spacing. Of these I drop 16,110 that are not covered by the construction data. Finally, following \cite{schoenholzer2022}, for the baseline versions of all specifications I restrict the sample to cities with no more than two lifetime switches.\footnote
{
This is to avoid creating an excessive amount of duplicate observations. Allowing more switches skews the sample towards cities that switch often. Keeping all cities and using only e.g. the first switch for each city skews it in favour of early switches. I relax this restriction in a robustness check.
} 
This removes another 9,975 observations, leaving 6,635 in the baseline sample.

@@

While this result may seem like evidence for omitted variable bias in the baseline estimate, that explanation is ultimately not plausible. To cause bias in Column (1) conflict incidents would need to be correlated both with the post-conquest dummy and with construction --- however, we can see that the latter is not the case: the coefficients on $Conflict$ in Columns (3) and (4) are tiny and not significant by any stretch of the imagination.\footnote
{
The coefficients on $Conflict$ in Table \ref{tab:controls_50y} are conditional correlations. Simply computing the correlation coefficient between the dummies for conflict incidents and for construction yields a value of $-0.01$.
} 
Rather, I suggest that the estimates for $\theta_{conquest}$ are different because they are estimated on different samples. More than two thirds of observations are lost between Columns (2) and (3) because of missing values in the $Conflict$ variable. Figure \ref{fig:conflict_map} shows that the remaining observations follow quite a different distribution across space --- if the spatial composition of the smaller sample was the same, the entire map would be a uniform shade. Instead we see big discrepancies: the west, the south, and Brandenburg retain 30\% to 60\% of their observations, while many northern and eastern regions all but vanish from the sample.

If we accept that the difference between the $\theta_{conquest}$ coefficients in (1) and (3) is due to the different spatial distribution of the sample, that has the interesting implication of spatially heterogeneous treatment effects. The null effect in (1) could be an average of the negative effect in the southwest and a hypothetical positive effect in the northeast. Outsiders could play a role, in a similar vein to \cite{levine2021, levine2022}'s theory: the south and the west are bordered by the Habsburg Empire and France, two stable major powers, while the northeast is somewhat sheltered by the North Sea, the Baltic Sea, and the territory that comprises 1937 Poland, which was fragmented throughout much of its history.\footnote
{
Of course, England and Sweden would attack via the North and Baltic seas, but it seems a reasonable assumption that competition for territory would be more intense between states that share a land border.
} 
BLANK \cite{cervellati2022}. I leave this for future research to explore.

I conduct a number of other robustness checks, which are summarised in the Appendix. Table \ref{tab:robustness_50y} contains regressions using different definitions of the sample and treatment. Columns (2) and (3) use larger samples that include cities with a higher number of lifetime switches. Column (4) shows the results of a regression in which the post-treatment dummy reverts back to 0 after 200 years. With this I intend to replicate the same event window as in Equation \eqref{eq:sw22} and to zero in on the effect over the first two centuries following a switch. While increasing the cutoff for lifetime switches increases the significance of the overall treatment effect (likely because the sample contains many duplicates of cities that switch often), none of these alternative specifications affect the estimates of the interactions.

@@

\clearpage
\section*{Appendix}

\setcounter{table}{0}
\renewcommand{\thetable}{A\arabic{table}}

\input{paper/output/regressions/robustness_50y}
